---
title: "Exercise"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
library(submitr)
library(gradethis)
library(tidyverse)

knitr::opts_chunk$set(echo = FALSE)
options(tutorial.storage = "none")
knitr::opts_chunk$set(exercise.checker = gradethis::grade_learnr)
```

## Intro 

The first thing you have to do is to log in.

```{r __login__,  context = "setup"}
instructor_key <- "isostats"
account_name <- "statprep.annie@gmail.com"
credentials <- 
  "password.csv"
 # "1WvQDD1sQHcc_aZ1eisWkZvhU4a3jEAR2HXt_1REojpM"

storage_actions <- in_local_file("submissions.csv")
```

<!--
child=system.file("submitr_login_script.Rmd", package = "submitr")}
-->

```{r child="submitr_login_script.Rmd"}
```

### Continue

Click on Next topic to start.

## Short text answers

## Overview

If you'd like users to submit open-ended answers, use a text box question.  Correct and incorrect answers will be matched exactly (including white space). A minimum of one correct answer is required.

Text value inputs are trimmed before they are compared to answers provided.

Here a `custum question_is_correct` function is used

```{r custom_class, echo = FALSE}
question_is_correct.always_correct <- function(question, value, ...) {
    return(learnr::mark_as(TRUE, NULL))
}

question(
  "Provide your answer",
  answer("answer", correct = TRUE),
  correct = "Answer Provided",
  allow_retry = TRUE,
  type = c("always_correct", "learnr_text")
)

```

If the user has to be able to modify answer, we have to trick learnr, by recording "incorrect" answers. Here is another version allowing this, unfortunately with bright red buttons.

```{r text_box, echo = FALSE}
question_text(
  "Provide your answer",
  answer("C0rrect", correct = TRUE),
  incorrect = "Ok",
  try_again_button = "Modify your answer",
  allow_retry = TRUE
)
```


## Topic One

```{r planets}
question("Which planet do we live on?",
         answer("Mars", correct=FALSE),
         answer("Earth", correct = TRUE,  message = "Good job Earthling!"),
         answer("Saturn",  correct = FALSE),
         allow_retry = TRUE,
         random_answer_order = TRUE
        )
```


## text

```{r textquestion}
question_text(
  "Please enter the word 'C0rrect' below:",
  answer("correct", message = "Don't forget to capitalize"),
  answer("c0rrect", message = "Don't forget to capitalize"),
  answer("Crorrect", message = "Is it really an 'o'?"),
  answer("C0rrect ", message = "Make sure you do not have a trailing space"),
  answer("Correct", correct = TRUE),
  allow_retry = TRUE,
  trim = FALSE
)
```

## `grade_result()`

###

`grade_result()` checks whether or not the student's code returns the correct result. It matches the result against one or more conditions and returns the message (and correct/incorrect status) associated with the first matched condition.

Here is an example of `grade_result()` in use.

* Calculate the average number of weeks in a month.

```{r grade_res, exercise = TRUE}

```

```{r grade_res-check}
grade_result(
  pass_if(str_length(.result) > 4, "Write some more")
)
```





## Topic Two
```{r}
text_check <- function(
  label,
  user_code,
  solution_code,
  check_code,
  envir_result,
  evaluate_result,
  envir_prep,
  ...
) {
  list(message = "Great job!", correct = TRUE, location = "append")
}

```

```{r enter-text, exercise=TRUE, exercise.cap = "Answer", exercise.lines = 10, exercise.diagnostics = FALSE, exercise.completion = FALSE}

```

```{r enter-text-check }

```


## Video

If I make this into an embedded video (by prepending the link with "bang!") the event recorder doesn't always work.

![Just a link](https://youtu.be/zNzZ1PfUDNk)

## Finishing

```{r finish}
question("Are you finished with the exercise?",
         answer("Yes", correct=TRUE),
         answer("No", correct=TRUE)
        )
```


